---
title: "Asessment 1"
author: "Kris Chavez (s4591950)"
date: '2022-05-03'
output: 
  html_document:
      number_sections: true           
      toc: true                       #TOC = Table of COntents
      toc_depth: 2
      theme: readable                  #Added a theme to make the document more appealing
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Install.packages("tidyverse")
# Install.packages("rmarkdown")
library(tidyverse)
library(rmarkdown)
```

# RMarkdown Editing

### What is RMarkdown?
__Rmarkdown__ is a tool mostly used by _analysts_, to present their findings in the most visually appealing way.  Rmarkdown has the ability to add diagrams, plots, images and formatting options to those wanting to use Rstudio's to compile and present data.


### Loading the dataset
As shown below, we have loaded the *data* in a **new** variable called 'fastfood'
```{r load the required CSV file}
# Set working the working directory to the data set provided by the lecturer
fastfood <- read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
```


### Saving a copy of the dataset
``` {r saving a  copy of the CSV file}
# Saving my data as a CSV file
write_csv(fastfood, "fastfood.csv")
fastfood_data<-read_csv("fastfood.csv")
```


### Filtering the dataset:
Given the criteria (dot points below), the goal of this assignment was to use _knitr_, _kable_ and the _head_ function to display visually appealing data.

+ Display the first __10 rows__ of the data set
+ Display the first __10 rows__ of the data set and the first __5 variables__.
```{r filtering the data}
# Display the first 10 rows of the data set
knitr::kable(head(fastfood, 10), "pipe")        # pipe function is used to format the table
# Display the first 10 rows of the data set and the first 5 variables
knitr::kable(head(fastfood[1:10, 1:5]), "pipe") 
```